Considering scale in multilayer animal social networks

### 2020-06-13 paper/manuscript.Rmd
lc result

Increasing land cover resolution resulted in a decreased availability of forage,
a rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats. Individuals in summer layers had consistent weak connections
(Figure \@ref(fig:lcres)a). Mean graph strength increased consistently in winter
forest and open habitats but varied in winter forage varied across land cover
resolutions with an increase at 250 m and decrease at 500 m (Figure
\@ref(fig:lcres)a). Layer relevance was stable for all habitat classes in summer
layers; layer relevance was significantly higher in winter and stable in open
and forest habitats but decreased for forage habitats (Figure
\@ref(fig:lcres)b). <!--This pattern during the winter indicates that
individuals had fewer neighbours in forage habitat habitats compared to their
overall neighbourhood across habitats, likely due to the patchy nature of
forage-->Layer similarity was low but stable for forest and open, except for a
sharp decrease in layer similarity in open at 100 m and 250 m (Figure
\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
summer and winter forage because, at all land cover resolutions greater than 30
m, there were no individuals connected in the network layers. Individuals still
used forage habitats, but given the lower availability due to increasing
land cover resolution, at a much lower rate. Connective redundancy was moderately
high but decreased slightly as land cover resolution increased, indicating that
many neighbours were the same between layers, but the proportion of neighbours
in each layer slightly decreased at increasing land cover resolutions (Figure
\@ref(fig:lcres)d). Overall, these results indicate the importance of matching
land cover resolution to scale of selection as well as ensuring the land cover
product used has a resolution fine enough to detect landscape features and
habitats relevant to study species, such as important patchy and rare habitats.

>>>>

Increasing land cover resolution resulted in a decreased availability of forage,
a rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
and edge overlap was relatively consistent across land cover resolutions for
forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
sharply between 30 m and 600 m in forage layers, afterwards remaining stable to
1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
forage layers across land cover resolutions than open and forest (Figure
\@ref(fig:lcres) D). The proportion of relocations in forest and open habitats
increased with increasing spatial resolution, while decreasing in forage habitat
(Supp. 1 <!-- todo-->).  Overall, these results indicate the importance of
matching land cover resolution to scale of selection as well as ensuring the
land cover product used has a resolution fine enough to detect landscape
features and habitats relevant to study species, such as important patchy and
rare habitats.
